---
title: "HUPS3"
author: "Chris Harris"
date: "Last edited: `r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<!-- Style definitions -->
<style type="text/css">
h1.title {
  text-align: center;
}
h4.author {
  text-align: center;
}
h4.date {
  text-align: center;
}
</style>

```{r init, include=FALSE}
# Setup -------------------------------------------------------------------

# Dependencies
if (!require(needs)) {install.packages("needs"); library(needs)}
if (!require(goallabr)) {
  if (!require(devtools)) {install.packages("devtools"); library(devtools)}
  install_github("chrisharrisUU/goallabr")
}
needs(BayesFactor, dplyr, ggplot2, ggsci, goallabr,
      gridExtra, here, kableExtra, magrittr, tidyr, papaja, purrr)
prioritize(dplyr)

source(here("Auxiliary/HUPS3_init.R"))

# Color palette for graphs
pal <- ggsci::pal_uchicago()(5)[c(3, 5, 1)]


# Functions ---------------------------------------------------------------

# Import functions from GitHub
# https://stackoverflow.com/a/35720824/10357426
source_https <- function(u, unlink.tmp.certs = FALSE) {
  # load package
  if (!require(RCurl)) {install.packages("RCurl"); library(RCurl)}
  
  # read script lines from website using a security certificate
  if (!file.exists(here("Auxiliary/cacert.pem"))) {
    download.file(url = "http://curl.haxx.se/ca/cacert.pem", destfile = here("Auxiliary/cacert.pem"))
  }
  script <- getURL(u, followlocation = TRUE, cainfo = here("Auxiliary/cacert.pem"))
  if (unlink.tmp.certs) {unlink(here("Auxiliary/cacert.pem"))}
  
  # parase lines and evealuate in the global environement
  eval(parse(text = script), envir = .GlobalEnv)
}
# My functions for outputting inference tests in APAish style
source_https("https://raw.githubusercontent.com/chrisharrisUU/testoutputs/master/functions.R")


# Canonical sorting -------------------------------------------------------

df3 <- df3_raw %>%
  # Recode primacy --> frequent option is right
  mutate(pref1_1 = ifelse(primacy == "right frequent", pref1_raw, 100 - pref1_raw),
         pref2_1 = ifelse(primacy == "right frequent", pref2_raw, 100 - pref2_raw),
         empl1_1 = ifelse(primacy == "right frequent", empl1_raw, (-1) * empl1_raw),
         empl2_1 = ifelse(primacy == "right frequent", empl2_raw, (-1) * empl2_raw),
         like1_1 = ifelse(primacy == "right frequent", like1_raw, (-1) * like1_raw),
         like2_1 = ifelse(primacy == "right frequent", like2_raw, (-1) * like2_raw)) %>%
  # Merge impression variable (only asked once)
  mutate(impr_l_raw = ifelse(order == "positive first", impr1_l_raw, impr2_l_raw),
         impr_r_raw = ifelse(order == "positive first", impr1_r_raw, impr2_r_raw)) %>%
  # Recode primacy --> frequent option is right for difference measures
  mutate(impr_1 = ifelse(primacy == "left frequent", impr_l_raw - impr_r_raw, impr_r_raw - impr_l_raw) / 100,
         cond1_1 = ifelse(primacy == "left frequent", cond1_l_raw - cond1_r_raw, cond1_r_raw - cond1_l_raw) / 100,
         cond2_1 = ifelse(primacy == "left frequent", cond2_l_raw - cond2_r_raw, cond2_r_raw - cond2_l_raw) / 100,
         conf1_1 = ifelse(primacy == "left frequent", conf1_l_raw - conf1_r_raw, conf1_r_raw - conf1_l_raw) / 100,
         conf2_1 = ifelse(primacy == "left frequent", conf2_l_raw - conf2_r_raw, conf2_r_raw - conf2_l_raw) / 100) %>%
  # Recode condition
  mutate(pref1_2     = ifelse(condition == "smiles", pref1_1, 100 - pref1_1),
         pref2_2     = ifelse(condition == "smiles", pref2_1, 100 - pref2_1),
         empl_pos    = ifelse(condition == "smiles", empl1_1, (-1) * empl1_1),
         empl_neg    = ifelse(condition == "smiles", empl2_1, (-1) * empl2_1),
         like_pos    = ifelse(condition == "smiles", like1_1, (-1) * like1_1),
         like_neg    = ifelse(condition == "smiles", like2_1, (-1) * like2_1),
         impr_dp     = ifelse(order == "positive first", impr_1, (-1) * impr_1),
         cond_pos_dp = ifelse(condition == "smiles", cond1_1, (-1) * cond1_1),
         cond_neg_dp = ifelse(condition == "smiles", cond2_1, (-1) * cond2_1),
         conf_pos_dp = ifelse(condition == "smiles", conf1_1, (-1) * conf1_1),
         conf_neg_dp = ifelse(condition == "smiles", conf2_1, (-1) * conf2_1)) %>%
  # Rescale
  mutate(pref_pos = pref1_2 - 50,
         pref_neg = pref2_2 - 50)

```

#   {.tabset .tabset-fade}

## Summary

The setup of the experiment was identical to the previous one (HUPS2). This time, however, we had two versions of the DVs in which one time the framing was positive (e.g., "Who of these two would you rather be around in a social setting?") and the other time the framing was negative (e.g., "Who of these two would you be more likely to avoid in a social setting?"). The order was counterbalanced. Following the initial evidence (see below), participants would either first encounter positively framed DVs or negatively framed DVs and thereafter the alternative.  

**Coding:** For now I collapsed over order. I recoded the data so that for DVs with the positive framing we expect higher values (e.g., > 0). For DVs with the negative framing we expect the opposite (thus < 0.  

.  
.  
.  

*From the previous experiment:*  
 
We had two conditions, one with many smiles one with many frowns.  

We counterbalanced whether participants saw two males or two females, which of two pairs (two pairs for each gender) they saw, who was shown left and who was shown right, and finally whether the left or the right person was the person shown more frequently.  

The distribution participants encountered was for the smiles condition:  

|          | Smiles | Frowns |  
|----------|--------|--------|  
| Person A |    9   |    3   |  
| Person B |    3   |    1   |  

For the frowns condition it was  

|          | Smiles | Frowns |  
|----------|--------|--------|  
| Person A |    3   |    9   |  
| Person B |    1   |    3   |  

After a short introduction ("In this study, we investigate how people form impressions of others. You will encounter two individuals a few times and then we will ask you some questions regarding these two individuals."), participants encountered the initial evidence, and then answered a number of DVs (the other tabs). The order of the tabs is also the order the DVs were asked. I tried to give an indication of what each DV looked like, but participants either had a binary choice in which they clicked on either of the two images. Or they cound indicate their estimate on a slider with the two images as anchors. 

## Likeability

*Who of these two would you rather be around in a social setting?*  
*Who of these two would you be more likely to avoid in a social setting?*  

(image left) (image right)

```{r}
df3 %>%
  mutate(like_cond_pos = case_when(condition == "smiles" & like_pos == 1 ~ "Smiles\nexpected\nbias",
                                   condition == "smiles" & like_pos == -1 ~ "Smiles\nunexpected\nbias",
                                   condition == "frowns" & like_pos == 1 ~ "Frowns\nexpected\nbias",
                                   condition == "frowns" & like_pos == -1 ~ "Frowns\nunexpected\nbias"),
         like_cond_neg = case_when(condition == "smiles" & like_neg == -1 ~ "Smiles\nexpected\nbias",
                                   condition == "smiles" & like_neg == 1 ~ "Smiles\nunexpected\nbias",
                                   condition == "frowns" & like_neg == -1 ~ "Frowns\nexpected\nbias",
                                   condition == "frowns" & like_neg == 1 ~ "Frowns\nunexpected\nbias")) %>%
  pivot_longer(cols = c("like_cond_pos", "like_cond_neg"),
               names_to = "posneg",
               values_to = "like_cond") %>%
  mutate(like_cond = factor(like_cond, levels = c("Smiles\nexpected\nbias",
                                                  "Smiles\nunexpected\nbias",
                                                  "Frowns\nexpected\nbias",
                                                  "Frowns\nunexpected\nbias"))) %>%
  mutate(posneg = factor(posneg, levels = c("like_cond_pos", "like_cond_neg"), labels = c("positive_framing", "negative_framing"))) %>%
  ggplot(aes(x = like_cond)) +
  geom_bar() +
  theme_apa() +
  labs(x = "Conditions",
       y = "Employability") +
  theme(legend.position = "none") +
  facet_wrap(~posneg)
```


## Preference


*Which of these two persons did you like more?*  
*Who of these two did you like less?*  

(image left) |-----------| (image right)

<p>&nbsp;</p>
<p>&nbsp;</p>
<p>&nbsp;</p>

```{r}
# Graph
df3 %>%
  pivot_longer(cols = c("pref_pos", "pref_neg"),
               names_to = "posneg",
               values_to = "pref") %>%
  mutate(posneg = factor(posneg, levels = c("pref_pos", "pref_neg"), labels = c("positive_framing", "negative_framing"))) %>%
  ggplot(aes(x = condition,
             y = pref,
             fill = condition)) +
  geom_violin() + 
  stat_summary(fun.data = "mean_sdl", geom = "crossbar", width = 0.2, fun.args = list(mult = 1)) +
  geom_jitter(size = 0.5, width = 0.2) +
  geom_hline(yintercept = 0, linetype = 2) +
  scale_fill_manual(values = pal) +
  theme_apa() +
  labs(x = "Condition",
       y = "Relative contingency estimates") +
  theme(legend.position = "none") +
  facet_wrap(~posneg + order)
```


```{r}
### Descriptives
df3 %>%
  pivot_longer(cols = c("pref_pos", "pref_neg"),
               names_to = "posneg",
               values_to = "pref") %>%
  mutate(posneg = factor(posneg, levels = c("pref_pos", "pref_neg"), labels = c("positive_framing", "negative_framing"))) %>%
  group_by(condition, posneg) %>%
  summarize(M = printnum(mean(pref)),
            SD = printnum(sd(pref))) %>%
  knitr::kable(caption = "Descriptives preference", digits = 2) %>%
  kable_styling(bootstrap_options = "hover", full_width = F, position = "center")
```


## Employability

*Who would you rather hire for a job that requires cooperation?*  
*Imagine you are working in a dangerous area and need to hire a personal bodyguard. Who of these two would you rather hire?*  

(image left) (image right)

<p>&nbsp;</p>
<p>&nbsp;</p>
<p>&nbsp;</p>


```{r}
df3 %>%
  mutate(like_empl_pos = case_when(condition == "smiles" & empl_pos == 1 ~ "Smiles\nexpected\nbias",
                                   condition == "smiles" & empl_pos == -1 ~ "Smiles\nunexpected\nbias",
                                   condition == "frowns" & empl_pos == 1 ~ "Frowns\nexpected\nbias",
                                   condition == "frowns" & empl_pos == -1 ~ "Frowns\nunexpected\nbias"),
         like_empl_neg = case_when(condition == "smiles" & empl_neg == -1 ~ "Smiles\nexpected\nbias",
                                   condition == "smiles" & empl_neg == 1 ~ "Smiles\nunexpected\nbias",
                                   condition == "frowns" & empl_neg == -1 ~ "Frowns\nexpected\nbias",
                                   condition == "frowns" & empl_neg == 1 ~ "Frowns\nunexpected\nbias")) %>%
  pivot_longer(cols = c("like_empl_pos", "like_empl_neg"),
               names_to = "posneg",
               values_to = "empl_cond") %>%
  mutate(empl_cond = factor(empl_cond, levels = c("Smiles\nexpected\nbias",
                                                  "Smiles\nunexpected\nbias",
                                                  "Frowns\nexpected\nbias",
                                                  "Frowns\nunexpected\nbias"))) %>%
  mutate(posneg = factor(posneg, levels = c("like_empl_pos", "like_empl_neg"), labels = c("positive_framing", "negative_framing"))) %>%
  ggplot(aes(x = empl_cond)) +
  geom_bar() +
  theme_apa() +
  labs(x = "Conditions",
       y = "Employability") +
  theme(legend.position = "none") +
  facet_wrap(~posneg)
```


## Impression

*On average, did this person seem more grumpy or more cheerful most of the time?*  
*On average, did this person seem more cheerful or more grumpy most of the time?*

Left : Grumpy |----------| Cheerful  
Right: Grumpy |----------| Cheerful  
*reversed for negative DV*  

```{r}
# Graph
df3 %>%
  ggplot(aes(x = condition,
             y = impr_dp,
             fill = condition)) +
  geom_violin() + 
  stat_summary(fun.data = "mean_sdl", geom = "crossbar", width = 0.2, fun.args = list(mult = 1)) +
  geom_jitter(size = 0.5, width = 0.2) +
  geom_hline(yintercept = 0, linetype = 2) +
  scale_fill_manual(values = pal) +
  theme_apa() +
  labs(x = "Condition",
       y = "Impression estimates") +
  theme(legend.position = "none") +
  facet_wrap(~order)
```

```{r}
### Descriptives
df3 %>%
  group_by(condition, order) %>%
  summarize(M = printnum(mean(impr_dp)),
            SD = printnum(sd(impr_dp))) %>%
  knitr::kable(caption = "Descriptives impression", digits = 2) %>%
  kable_styling(bootstrap_options = "hover", full_width = F, position = "center")
```


## Conditional estimates

*How likely (in %) was it that if you encountered... ....XXX, they smiled/frowned?*  

Left : 0 |----------| 100  
Right: 0 |----------| 100  

<p>&nbsp;</p>
<p>&nbsp;</p>
<p>&nbsp;</p>

```{r}
df3 %>%
  pivot_longer(cols = c("cond_pos_dp", "cond_neg_dp"),
               names_to = "posneg",
               values_to = "cond_dp") %>%
  mutate(posneg = factor(posneg, levels = c("cond_pos_dp", "cond_neg_dp"), labels = c("positive_framing", "negative_framing"))) %>%
  ggplot(aes(x = condition,
             y = cond_dp,
             fill = condition)) +
  geom_violin() + 
  stat_summary(fun.data = "mean_sdl", geom = "crossbar", width = 0.2, fun.args = list(mult = 1)) +
  geom_jitter(size = 0.5, width = 0.2) +
  geom_hline(yintercept = 0, linetype = 2) +
  scale_fill_manual(values = pal) +
  theme_apa() +
  labs(x = "Condition",
       y = "Conditional probability estimates") +
  theme(legend.position = "none") +
  facet_wrap(~posneg + order)
```


```{r}
### Descriptives
df3 %>%
  pivot_longer(cols = c("cond_pos_dp", "cond_neg_dp"),
               names_to = "posneg",
               values_to = "cond_dp") %>%
  mutate(posneg = factor(posneg, levels = c("cond_pos_dp", "cond_neg_dp"), labels = c("positive_framing", "negative_framing"))) %>%
  group_by(condition, posneg) %>%
  summarize(M = printnum(mean(cond_dp)),
            SD = printnum(sd(cond_dp))) %>%
  knitr::kable(caption = "Conditional probability estimates", digits = 2) %>%
  kable_styling(bootstrap_options = "hover", full_width = F, position = "center")
```


## Confidence

*How confident (in %) are you that you can make a reasonable estimate?*

Left : 0 |----------| 100  
Right: 0 |----------| 100  

```{r}
# Graph
df3 %>%
  pivot_longer(cols = c("conf_pos_dp", "conf_neg_dp"),
               names_to = "posneg",
               values_to = "conf_dp") %>%
  mutate(posneg = factor(posneg, levels = c("conf_pos_dp", "conf_neg_dp"), labels = c("positive_framing", "negative_framing"))) %>%
  ggplot(aes(x = condition,
             y = conf_dp,
             fill = condition)) +
  geom_violin() + 
  stat_summary(fun.data = "mean_sdl", geom = "crossbar", width = 0.2, fun.args = list(mult = 1)) +
  geom_jitter(size = 0.5, width = 0.2) +
  geom_hline(yintercept = 0, linetype = 2) +
  scale_fill_manual(values = pal) +
  theme_apa() +
  labs(x = "Condition",
       y = "Confidence estimates") +
  theme(legend.position = "none") +
  facet_wrap(~posneg)
```

```{r}
### Descriptives
df3 %>%
  pivot_longer(cols = c("conf_pos_dp", "conf_neg_dp"),
               names_to = "posneg",
               values_to = "conf_dp") %>%
  group_by(condition, posneg) %>%
  summarize(M = printnum(mean(conf_dp)),
            SD = printnum(sd(conf_dp))) %>%
  knitr::kable(caption = "Confidence estimates", digits = 2) %>%
  kable_styling(bootstrap_options = "hover", full_width = F, position = "center")
```


## Demographic data

Our participants:
```{r}
# Summary of most relevant demographic data
df3 %>%
  summarise(N = n(),
            female = length(which(gender == "female")),
            age_mean = mean(age, na.rm = TRUE),
            age_sd = sd(age, na.rm = TRUE),
            Psychstudents_percent = length(which(psych == "Yes")) / n() * 100) %>%
  knitr::kable(caption = "Demographic data", digits = 2) %>%
  kable_styling(bootstrap_options = "hover", full_width = F, position = "center")
```

And their level of education:
```{r}
# Level of education
df3 %>%
  group_by(edu) %>%
  summarise(count = length(edu)) %>%
  knitr::kable(caption = "Level of education", digits = 2) %>%
  kable_styling(bootstrap_options = "hover", full_width = F, position = "center")
```

## Counterbalancing check

This tab is mainly for me to make sure I got the recoding of all the counterbalancing right.

Regression of recoded factors on raw scores:  

Preference
```{r}
# Preference
lm(pref_pos ~ condition, data = df3) %>%
  summary()
lm(pref1_raw ~ condition * primacy, data = df3_raw) %>%
  summary()

lm(pref_neg ~ condition, data = df3) %>%
  summary()
lm(pref2_raw ~ condition * primacy, data = df3_raw) %>%
  summary()
```

Conditionals
```{r}
lm(cond_pos_dp ~ condition, data = df3) %>%
  summary()
lm((cond1_l_raw - cond1_r_raw) ~ condition * primacy, data = df3_raw) %>%
  summary()

lm(cond_neg_dp ~ condition, data = df3) %>%
  summary()
lm((cond2_l_raw - cond2_r_raw) ~ condition * primacy, data = df3_raw) %>%
  summary()
```

