---
title: "Pretest HUPS"
author: "Chris Harris"
date: "Last edited: `r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<!-- Style definitions -->
<style type="text/css">
h1.title {
  text-align: center;
}
h4.author {
  text-align: center;
}
h4.date {
  text-align: center;
}
</style>

```{r init, include=FALSE}
### Setup----
# Dependencies
if (!require(needs)) {install.packages("needs"); library(needs)}
if (!require(goallabr)) {
  if (!require(devtools)) {install.packages("devtools"); library(devtools)}
  install_github("chrisharrisUU/goallabr")
}
needs(BayesFactor, dplyr, ggplot2, goallabr, gridExtra,
      here, kableExtra, magrittr, tidyr, papaja, purrr)
prioritize(dplyr)

source(here("Auxiliary/HUPS1_init.R"))

### Functions----


### Canonical sorting----
df1 <- do_counterbalance(df1)
```

#   {.tabset .tabset-fade}

## Frequency


*Which of these two people did you encounter more often?*

[image left] [image right]

<p>&nbsp;</p>
<p>&nbsp;</p>
<p>&nbsp;</p>

```{r, include=FALSE}
freq_long <- df1 %>%
  select(freq_rich, freq_imp, participant.id) %>%
  gather(key = "cond",
         value = "freq",
         c(freq_rich, freq_imp)) %>%
  mutate(cond = ifelse(cond == "freq_rich", "rich", "imp")) %>%
  mutate(cond = factor(cond, levels = c("rich", "imp"))) %>%
  mutate(freq = ifelse(freq == 1, freq, 0))
```


Most people correctly identify which person was shown more frequently. Only on three instances did participants get this wrong:

```{r}
freq_long %>%
  filter(freq == 0) %>%
  knitr::kable(caption = "Instances in which frequency is wrong", digits = 2) %>%
  kable_styling(bootstrap_options = "hover", full_width = F, position = "center")
```

Here the percentage scores of correct instances per condition:

```{r}
freq_long %>%
  group_by(cond) %>%
  summarize(avg = mean(freq)) %>%
  knitr::kable(caption = "Instances correctly identified", digits = 2) %>%
  kable_styling(bootstrap_options = "hover", full_width = F, position = "center")
```


These do not differ from one another:

```{r, results='asis'}
distr <- table(freq_long$cond, freq_long$freq)

testBF <- proportionBF(y = distr["rich", "1"],
             N = distr["rich", "1"] + distr["rich", "0"],
             p = distr["imp", "1"] / (distr["imp", "1"] + distr["imp", "0"]),
             rscale = "ultrawide",
             nullInterval = c(0, 1)) %>%
  printBFb(print = TRUE)
testFR <- binom.test(x = distr["rich", "1"],
           n = distr["rich", "1"] + distr["rich", "0"],
           p = distr["imp", "1"] / (distr["imp", "1"] + distr["imp", "0"]),
           alternative = "two.sided")

paste0(testBF, ", *p* = ", printnum(testFR$p.value))
```


## Preference

*Which of these two people seemed happier to you?*

[image left] [image right]

<p>&nbsp;</p>
<p>&nbsp;</p>
<p>&nbsp;</p>

```{r, include=FALSE}
pref_long <- df1 %>%
  select(pref_rich, pref_imp) %>%
  gather(key = "cond",
         value = "pref",
         c(pref_rich, pref_imp)) %>%
  mutate(cond = ifelse(cond == "pref_rich", "rich", "imp")) %>%
  mutate(cond = factor(cond, levels = c("rich", "imp")))
```

Preference was coded as -1 or +1 with the frequent option always being +1.  
There was a general preference for the *frequent* option as seen here:

```{r}
pref_long %>%
  group_by(cond) %>%
  summarize(avg = mean(pref)) %>%
  knitr::kable(caption = "Average preference", digits = 2) %>%
  kable_styling(bootstrap_options = "hover", full_width = F, position = "center")
```

These, surprisingly, do not differ from one another:
```{r, results='asis'}
distr <- table(pref_long$cond, pref_long$pref)

testBF <- proportionBF(y = distr["rich", "1"],
                       N = distr["rich", "1"] + distr["rich", "-1"],
                       p = distr["imp", "1"] / (distr["imp", "1"] + distr["imp", "-1"]),
                       rscale = "ultrawide",
                       nullInterval = c(0, 1)) %>%
  printBFb(print = TRUE)
testFR <- binom.test(x = distr["rich", "1"],
                     n = distr["rich", "1"] + distr["rich", "-1"],
                     p = distr["imp", "1"] / (distr["imp", "1"] + distr["imp", "-1"]),
                     alternative = "two.sided")

paste0(testBF, ", *p* = ", printnum(testFR$p.value))
```

But also do not differ meaningfully from 0:
```{r, results='asis'}
distr <- table(pref_long$pref)

testBF <- proportionBF(y = distr["1"],
                       N = distr["1"] + distr["-1"],
                       p = .5,
                       rscale = "ultrawide",
                       nullInterval = c(.5, 1)) %>%
  printBFb(print = TRUE)
testFR <- binom.test(x = distr["1"],
                     n = distr["1"] + distr["-1"],
                     p = .5,
                     alternative = "greater")

paste0(testBF, ", *p* = ", printnum(testFR$p.value))
```


## Conditional estimates

*On average, did this person smile or frown more often?*

Left : Frown |----------| Smile  
Right: Frown |----------| Smile  

<p>&nbsp;</p>
<p>&nbsp;</p>
<p>&nbsp;</p>

```{r, include=FALSE}
cond_long <- rbind(
  df1 %>%
    select(cond_rich_fr, cond_rich_in) %>%
    gather(key = "frequency",
           value = "value",
           c(cond_rich_fr, cond_rich_in)) %>%
    mutate(frequency = ifelse(frequency == "cond_rich_fr", "freq", "infr")) %>%
    mutate(frequency = factor(frequency, levels = c("freq", "infr")),
           cond = "rich"),
  df1 %>%
    select(cond_imp_fr, cond_imp_in) %>%
    gather(key = "frequency",
           value = "value",
           c(cond_imp_fr, cond_imp_in)) %>%
    mutate(frequency = ifelse(frequency == "cond_imp_fr", "freq", "infr")) %>%
    mutate(frequency = factor(frequency, levels = c("freq", "infr")),
           cond = "imp")
) %>%
  mutate(cond = factor(cond, levels = c("rich", "imp")))
```

Here (scale: 0 - 100) are the conditional estimates participants made:

```{r}
cond_long %>%
  group_by(cond, frequency) %>%
  summarize(avg = mean(value)) %>%
  knitr::kable(caption = "Conditional estimates", digits = 2) %>%
  kable_styling(bootstrap_options = "hover", full_width = F, position = "center")
```

```{r}
cond_long %>%
  ggplot(aes(x = cond,
             y = value,
             fill = frequency)) +
  geom_boxplot() +
  scale_fill_brewer(palette = "Dark2") +
  theme_apa()
```

These estimates result in the following &Delta;p-scores:
```{r}
df1 %>%
  mutate(rich = (cond_rich_fr - cond_rich_in) / 100,
         imp  = (cond_imp_fr - cond_imp_in) / 100) %>%
  summarize(rich = mean(rich),
            imp  = mean(imp)) %>%
  knitr::kable(caption = "dp-scores", digits = 2) %>%
  kable_styling(bootstrap_options = "hover", full_width = F, position = "center")
```

The two conditions do not differ from one another:
```{r, results='asis'}
df1 %>%
  mutate(rich_dp = (cond_rich_fr - cond_rich_in) / 100,
         imp_dp  = (cond_imp_fr - cond_imp_in) / 100) %$%
  ttestBF(x = rich_dp,
          y = imp_dp,
          nullInterval = c(-Inf, Inf),
          paired = TRUE) %>%
  printBFt(print = TRUE)
```

This is surprising, as we would have expected smiling to be associated with the frequent person in the reward-rich condition, but with the infrequent person in the reward-impoverished condition.

There is an overall difference from 0:
```{r, results='asis'}
df1 %>%
  mutate(rich_dp = (cond_rich_fr - cond_rich_in) / 100,
         imp_dp  = (cond_imp_fr - cond_imp_in) / 100) %>%
  select(rich_dp, imp_dp) %>%
  gather(key = "cond",
         value = "dp") %$%
  ttestBF(dp,
          mu = 0,
          nullInterval = c(0, Inf)) %>%
  printBFt(print = TRUE)
```


## Demographic data

Our participants:
```{r}
# Summary of most relevant demographic data
df1 %>%
  summarise(N = n(),
            female = length(which(gender == "female")),
            age_mean = mean(age, na.rm = TRUE),
            age_sd = sd(age, na.rm = TRUE),
            Psychstudents_percent = length(which(psych == "Yes")) / n() * 100) %>%
  knitr::kable(caption = "Demographic data", digits = 2) %>%
  kable_styling(bootstrap_options = "hover", full_width = F, position = "center")
```

And their level of education:
```{r}
# Level of education
df1 %>%
  group_by(edu) %>%
  summarise(count = length(edu)) %>%
  knitr::kable(caption = "Level of education", digits = 2) %>%
  kable_styling(bootstrap_options = "hover", full_width = F, position = "center")
```

## Counterbalancing

In this preliminary analyses I ignore gender (do we first show men or first show women), as well as which male/female individual is shown frequently and which is shown infrequently.

The logic is as follows:  

* Make the frequently shown face always the +1 (right) option  
* Link with condition  

And for the conditional estimates: 

* Determine frequently and infrequently shown option  
* Link with condition  

```{r eval=FALSE}
df %>%
    # Ignore Order-Women and Order-Men. There should be no difference
    #  2(condition: rich-imp vs. imp-rich, within)
    # x2(primacy: left-right vs. right-left frequent)
    # Preference
    # 1: Frequent = 1, infrequent = -1
    mutate(pref1_raw2 = ifelse(primacy == "left frequent", pref1_raw * (-1), pref1_raw),
           freq1_raw2 = ifelse(primacy == "left frequent", freq1_raw * (-1), freq1_raw),
           
           pref2_raw2 = ifelse(primacy == "left frequent", pref2_raw,        pref2_raw * (-1)),
           freq2_raw2 = ifelse(primacy == "left frequent", freq2_raw,        freq2_raw * (-1))) %>%
    # 2: assign condition
    mutate(pref_rich = ifelse(condition == "rich", pref1_raw2, pref2_raw2),
           pref_imp  = ifelse(condition == "rich", pref2_raw2, pref1_raw2),
           
           freq_rich = ifelse(condition == "rich", freq1_raw2, freq2_raw2),
           freq_imp  = ifelse(condition == "rich", freq2_raw2, freq1_raw2)) %>%
    # Conditionals
    # 1: frequently vs. infrequently shown
    mutate(cond_first_freq = ifelse(primacy == "left frequent", cond1_raw, cond2_raw),
           cond_first_infr = ifelse(primacy == "left frequent", cond2_raw, cond1_raw),
           
           cond_secon_freq = ifelse(primacy == "left frequent", cond4_raw, cond3_raw),
           cond_secon_infr = ifelse(primacy == "left frequent", cond3_raw, cond4_raw)) %>%
    # 2: assign condition
    mutate(cond_rich_fr = ifelse(condition == "rich", cond_first_freq, cond_secon_freq),
           cond_rich_in = ifelse(condition == "rich", cond_first_infr, cond_secon_infr),
           
           cond_imp_fr  = ifelse(condition == "rich", cond_secon_freq, cond_first_freq),
           cond_imp_in  = ifelse(condition == "rich", cond_secon_infr, cond_first_infr))
```

