---
title: "HUPS2"
author: "Chris Harris"
date: "Last edited: `r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<!-- Style definitions -->
<style type="text/css">
h1.title {
  text-align: center;
}
h4.author {
  text-align: center;
}
h4.date {
  text-align: center;
}
</style>

```{r init, include=FALSE}
# Setup -------------------------------------------------------------------

# Dependencies
if (!require(needs)) {install.packages("needs"); library(needs)}
if (!require(goallabr)) {
  if (!require(devtools)) {install.packages("devtools"); library(devtools)}
  install_github("chrisharrisUU/goallabr")
}
needs(BayesFactor, dplyr, ggplot2, ggsci, goallabr,
      gridExtra, here, kableExtra, magrittr, tidyr, papaja, purrr)
prioritize(dplyr)

source(here("Auxiliary/HUPS2_init.R"))

# Color palette for graphs
pal <- ggsci::pal_uchicago()(5)[c(3, 5, 1)]


# Functions ---------------------------------------------------------------

# Import functions from GitHub
# https://stackoverflow.com/a/35720824/10357426
source_https <- function(u, unlink.tmp.certs = FALSE) {
  # load package
  if (!require(RCurl)) {install.packages("RCurl"); library(RCurl)}
  
  # read script lines from website using a security certificate
  if (!file.exists(here("Auxiliary/cacert.pem"))) {
    download.file(url = "http://curl.haxx.se/ca/cacert.pem", destfile = here("Auxiliary/cacert.pem"))
  }
  script <- getURL(u, followlocation = TRUE, cainfo = here("Auxiliary/cacert.pem"))
  if (unlink.tmp.certs) {unlink(here("Auxiliary/cacert.pem"))}
  
  # parase lines and evealuate in the global environement
  eval(parse(text = script), envir = .GlobalEnv)
}
# My functions for outputting inference tests in APAish style
source_https("https://raw.githubusercontent.com/chrisharrisUU/testoutputs/master/functions.R")


# Canonical sorting -------------------------------------------------------

df2 <- df2_raw %>%
    # Recode primacy --> frequent option is right
    mutate(pref1 = ifelse(primacy == "right frequent", pref_raw, 100 - pref_raw),
           empl1 = ifelse(primacy == "right frequent", empl_raw, (-1) * empl_raw),
           like1 = ifelse(primacy == "right frequent", like_raw, (-1) * like_raw)) %>%
    # Recode condition
    mutate(pref2 = ifelse(condition == "smiles", pref1, 100 - pref1),
           empl = ifelse(condition == "smiles", empl1, (-1) * empl1),
           like = ifelse(condition == "smiles", like1, (-1) * like1)) %>%
    mutate(impr_dp = case_when(condition == "smiles" & primacy == "left frequent"  ~ (impr_l_raw - impr_r_raw) / 100,
                               condition == "smiles" & primacy == "right frequent" ~ (impr_r_raw - impr_l_raw) / 100,
                               condition == "frowns" & primacy == "left frequent"  ~ (impr_r_raw - impr_l_raw) / 100,
                               condition == "frowns" & primacy == "right frequent" ~ (impr_l_raw - impr_r_raw) / 100),
           cond_dp = case_when(condition == "smiles" & primacy == "left frequent"  ~ (cond_l_raw - cond_r_raw) / 100,
                               condition == "smiles" & primacy == "right frequent" ~ (cond_r_raw - cond_l_raw) / 100,
                               condition == "frowns" & primacy == "left frequent"  ~ (cond_r_raw - cond_l_raw) / 100,
                               condition == "frowns" & primacy == "right frequent" ~ (cond_l_raw - cond_r_raw) / 100),
           conf_dp = case_when(condition == "smiles" & primacy == "left frequent"  ~ (conf_l_raw - conf_r_raw) / 100,
                               condition == "smiles" & primacy == "right frequent" ~ (conf_r_raw - conf_l_raw) / 100,
                               condition == "frowns" & primacy == "left frequent"  ~ (conf_r_raw - conf_l_raw) / 100,
                               condition == "frowns" & primacy == "right frequent" ~ (conf_l_raw - conf_r_raw) / 100)) %>%
    # Rescale
    mutate(pref = pref2 - 50)

```

#   {.tabset .tabset-fade}

## Summary

[Here](https://www.soscisurvey.de/hups2/?act=6V57JPRSRHTwggCGuPqrFBGy) is a current link to the pretest. This pretest version allows you to skip pages by using that yellow bar in the top. Make sure to definitely visit the second page on which all parameters get initialized.

We had two conditions, one with many smiles one with many frowns.

We counterbalanced whether participants saw two males or two females, which of two pairs (two pairs for each gender) they saw, who was shown left and who was shown right, and finally whether the left or the right person was the person shown more frequently.  

The distribution participants encountered was for the smiles condition:  

|          | Smiles | Frowns |  
|----------|--------|--------|  
| Person A |    9   |    3   |  
| Person B |    3   |    1   |  

For the frowns condition it was  

|          | Smiles | Frowns |  
|----------|--------|--------|  
| Person A |    3   |    9   |  
| Person B |    1   |    3   |  

After a short introduction ("In this study, we investigate how people form impressions of others. You will encounter two individuals a few times and then we will ask you some questions regarding these two individuals."), participants encountered the initial evidence, and then answered a number of DVs (the other tabs). The order of the tabs is also the order the DVs were asked. I tried to give an indication of what each DV looked like, but participants either had a binary choice in which they clicked on either of the two images. Or they cound indicate their estimate on a slider with the two images as anchors. 

## Likeability

*Who of these two would you rather be around for an evening?*

(image left) (image right)

```{r}
df2 %>%
  mutate(like_cond = case_when(condition == "smiles" & like == 1 ~ "Smiles\nexpected\nbias",
                               condition == "smiles" & like == -1 ~ "Smiles\nunexpected\nbias",
                               condition == "frowns" & like == 1 ~ "Frowns\nexpected\nbias",
                               condition == "frowns" & like == -1 ~ "Frowns\nunexpected\nbias")) %>%
  mutate(like_cond = factor(like_cond, levels = c("Smiles\nexpected\nbias",
                                                  "Smiles\nunexpected\nbias",
                                                  "Frowns\nexpected\nbias",
                                                  "Frowns\nunexpected\nbias"))) %>%
  ggplot(aes(x = like_cond)) +
  geom_bar() +
  theme_apa() +
  labs(x = "Conditions",
       y = "Likeability") +
  theme(legend.position = "none")
```

```{r}
df2 %>%
  mutate(like = factor(like, levels = c(-1, 1), labels = c("unexpected", "expected"))) %$%
  table(condition, like) %>%
  knitr::kable(caption = "Descriptives likeability", digits = 2) %>%
  kable_styling(bootstrap_options = "hover", full_width = F, position = "center")
```

Smiles
```{r}
# Distribution
distr_like <- df2 %>%
  mutate(like = ifelse(like == 1, 1, 0)) %$%
  table(like, condition)
distr_like

# Tests
# Smiles
proportionBF(y = distr_like["1", "smiles"],
             N = distr_like["1", "smiles"] + distr_like["0", "smiles"],
             p = .5,
             rscale = "ultrawide",
             nullInterval = c(.5, 1)) %>% printBFb()
binom.test(x = distr_like["1", "smiles"],
           n = distr_like["1", "smiles"] + distr_like["0", "smiles"],
           p = .5,
           alternative = "greater")
```

Frowns
```{r}
# Frowns
proportionBF(y = distr_like["1", "frowns"],
             N = distr_like["1", "frowns"] + distr_like["0", "frowns"],
             p = .5,
             rscale = "ultrawide",
             nullInterval = c(.5, 1)) %>% printBFb()
binom.test(x = distr_like["1", "frowns"],
           n = distr_like["1", "frowns"] + distr_like["0", "frowns"],
           p = .5,
           alternative = "greater")
```


## Preference


*Which of these two persons did you like more?*

(image left) |-----------| (image right)

<p>&nbsp;</p>
<p>&nbsp;</p>
<p>&nbsp;</p>

```{r}
# Graph
df2 %>%
  ggplot(aes(x = condition,
             y = pref,
             fill = condition)) +
  geom_violin() + 
  stat_summary(fun.data = "mean_sdl", geom = "crossbar", width = 0.2, fun.args = list(mult = 1)) +
  geom_jitter(size = 0.5, width = 0.2) +
  geom_hline(yintercept = 0, linetype = 2) +
  scale_fill_manual(values = pal) +
  theme_apa() +
  labs(x = "Condition",
       y = "Relative contingency estimates") +
  theme(legend.position = "none")
```


```{r}
### Descriptives
df2 %>%
  group_by(condition) %>%
  summarize(M = printnum(mean(pref)),
            SD = printnum(sd(pref))) %>%
  knitr::kable(caption = "Descriptives preference", digits = 2) %>%
  kable_styling(bootstrap_options = "hover", full_width = F, position = "center")
```

Smiles
```{r}
# Smiles
df2 %>%
  filter(condition == "smiles") %>%
  as.data.frame() %$%
  ttestBF(pref,
          mu = 0,
          nullInterval = c(0, Inf)) %>%
  printBFt()
ttest(data = df2,
      y = pref,
      x = condition,
      mu = 0,
      sub = "smiles",
      dir = "greater")
```

Frowns
```{r}
# Frowns
df2 %>%
  filter(condition == "frowns") %>%
  as.data.frame() %$%
  ttestBF(pref,
          mu = 0,
          nullInterval = c(0, Inf)) %>%
  printBFt()
ttest(data = df2,
      y = pref,
      x = condition,
      mu = 0,
      sub = "frowns",
      dir = "greater")
```

Strength
```{r}
# Strength
df2 %>%
  as.data.frame() %>%
  ttestBF(formula = pref ~ condition,
          nullInterval = c(-Inf, Inf),
          data = .) %>%
  printBFt()
ttest(data = df2,
      y = pref,
      x = condition,
      dir = "two.sided")
```

Overall
```{r}
## Overall
df2 %>%
  as.data.frame() %$%
  ttestBF(pref,
          mu = 0,
          nullInterval = c(0, Inf)) %>%
  printBFt()
ttest(data = df2,
      y = pref,
      x = condition,
      mu = 0,
      dir = "greater")
```


## Employability

*Imagine you are responsible for a small team of employees. Who would you rather hire?*

(image left) (image right)

<p>&nbsp;</p>
<p>&nbsp;</p>
<p>&nbsp;</p>

There is a 100% match between the two dichotomous variables (likeability and employability), *r* = `r cor(df2$like, df2$empl)`.


```{r}
df2 %>%
  mutate(empl_cond = case_when(condition == "smiles" & like == 1 ~ "Smiles\nexpected\nbias",
                               condition == "smiles" & like == -1 ~ "Smiles\nunexpected\nbias",
                               condition == "frowns" & like == 1 ~ "Frowns\nexpected\nbias",
                               condition == "frowns" & like == -1 ~ "Frowns\nunexpected\nbias")) %>%
  mutate(empl_cond = factor(empl_cond, levels = c("Smiles\nexpected\nbias",
                                                  "Smiles\nunexpected\nbias",
                                                  "Frowns\nexpected\nbias",
                                                  "Frowns\nunexpected\nbias"))) %>%
  ggplot(aes(x = empl_cond)) +
  geom_bar() +
  theme_apa() +
  labs(x = "Conditions",
       y = "Employability") +
  theme(legend.position = "none")

```


```{r}
df2 %>%
  mutate(empl = factor(empl, levels = c(-1, 1), labels = c("unexpected", "expected"))) %$%
  table(condition, empl) %>%
  knitr::kable(caption = "Occurences Employability", digits = 2) %>%
  kable_styling(bootstrap_options = "hover", full_width = F, position = "center")
```

Smiles
```{r}
## Binary
# Distribution
distr_empl <- df2 %>%
  mutate(empl = ifelse(empl == 1, 1, 0)) %$%
  table(empl, condition)

# Tests
proportionBF(y = distr_empl["1", "smiles"],
             N = distr_empl["1", "smiles"] + distr_empl["0", "smiles"],
             p = .5,
             rscale = "ultrawide",
             nullInterval = c(.5, 1)) %>% printBFb()
binom.test(x = distr_empl["1", "smiles"],
           n = distr_empl["1", "smiles"] + distr_empl["0", "smiles"],
           p = .5,
           alternative = "greater")
```

Frowns
```{r}
proportionBF(y = distr_empl["1", "frowns"],
             N = distr_empl["1", "frowns"] + distr_empl["0", "frowns"],
             p = .5,
             rscale = "ultrawide",
             nullInterval = c(.5, 1)) %>% printBFb()
binom.test(x = distr_empl["1", "frowns"],
           n = distr_empl["1", "frowns"] + distr_empl["0", "frowns"],
           p = .5,
           alternative = "greater")
```


## Impression

*On average, did this person seem more grumpy or more cheerful most of the time?*

Left : Grumpy |----------| Cheerful  
Right: Grumpy |----------| Cheerful  

```{r}
# Graph
df2 %>%
  ggplot(aes(x = condition,
             y = impr_dp,
             fill = condition)) +
  geom_violin() + 
  stat_summary(fun.data = "mean_sdl", geom = "crossbar", width = 0.2, fun.args = list(mult = 1)) +
  geom_jitter(size = 0.5, width = 0.2) +
  geom_hline(yintercept = 0, linetype = 2) +
  scale_fill_manual(values = pal) +
  theme_apa() +
  labs(x = "Condition",
       y = "Impression estimates") +
  theme(legend.position = "none")
```

```{r}
### Descriptives
df2 %>%
  group_by(condition) %>%
  summarize(M = printnum(mean(impr_dp)),
            SD = printnum(sd(impr_dp))) %>%
  knitr::kable(caption = "Descriptives impression", digits = 2) %>%
  kable_styling(bootstrap_options = "hover", full_width = F, position = "center")
```

Smiles
```{r}
# Smiles
df2 %>%
  filter(condition == "smiles") %>%
  as.data.frame() %$%
  ttestBF(impr_dp,
          mu = 0,
          nullInterval = c(0, Inf)) %>%
  printBFt()
ttest(data = df2,
      y = impr_dp,
      x = condition,
      mu = 0,
      sub = "smiles",
      dir = "greater")
```

Frowns
```{r}
# Frowns
df2 %>%
  filter(condition == "frowns") %>%
  as.data.frame() %$%
  ttestBF(impr_dp,
          mu = 0,
          nullInterval = c(0, Inf)) %>%
  printBFt()
ttest(data = df2,
      y = impr_dp,
      x = condition,
      mu = 0,
      sub = "frowns",
      dir = "greater")
```

Strength
```{r}
# Strength
df2 %>%
  as.data.frame() %>%
  ttestBF(formula = impr_dp ~ condition,
          nullInterval = c(-Inf, Inf),
          data = .) %>%
  printBFt()
ttest(data = df2,
      y = impr_dp,
      x = condition,
      dir = "two.sided")
```

Overall
```{r}
## Overall
df2 %>%
  as.data.frame() %$%
  ttestBF(impr_dp,
          mu = 0,
          nullInterval = c(0, Inf)) %>%
  printBFt()
ttest(data = df2,
      y = impr_dp,
      x = condition,
      mu = 0,
      dir = "greater")
```


## Conditional estimates

*How likely (in %) was it that if you encountered... ....XXX, they smiled?*

Left : 0 |----------| 100  
Right: 0 |----------| 100  

<p>&nbsp;</p>
<p>&nbsp;</p>
<p>&nbsp;</p>

```{r}
df2 %>%
  ggplot(aes(x = condition,
             y = cond_dp,
             fill = condition)) +
  geom_violin() + 
  stat_summary(fun.data = "mean_sdl", geom = "crossbar", width = 0.2, fun.args = list(mult = 1)) +
  geom_jitter(size = 0.5, width = 0.2) +
  geom_hline(yintercept = 0, linetype = 2) +
  scale_fill_manual(values = pal) +
  theme_apa() +
  labs(x = "Condition",
       y = "Conditional probability estimates") +
  theme(legend.position = "none")
```


```{r}
### Descriptives
df2 %>%
  group_by(condition) %>%
  summarize(M = printnum(mean(cond_dp)),
            SD = printnum(sd(cond_dp))) %>%
  knitr::kable(caption = "Conditional probability estimates", digits = 2) %>%
  kable_styling(bootstrap_options = "hover", full_width = F, position = "center")
```

Smiles
```{r}
# Smiles
df2 %>%
  filter(condition == "smiles") %>%
  as.data.frame() %$%
  ttestBF(cond_dp,
          mu = 0,
          nullInterval = c(0, Inf)) %>%
  printBFt()
ttest(data = df2,
      y = cond_dp,
      x = condition,
      mu = 0,
      sub = "smiles",
      dir = "greater")
```

Frowns
```{r}
# Frowns
df2 %>%
  filter(condition == "frowns") %>%
  as.data.frame() %$%
  ttestBF(cond_dp,
          mu = 0,
          nullInterval = c(0, Inf)) %>%
  printBFt()
ttest(data = df2,
      y = cond_dp,
      x = condition,
      mu = 0,
      sub = "frowns",
      dir = "greater")
```

Strength
```{r}
# Strength
df2 %>%
  as.data.frame() %>%
  ttestBF(formula = cond_dp ~ condition,
          nullInterval = c(-Inf, Inf),
          data = .) %>%
  printBFt()
ttest(data = df2,
      y = cond_dp,
      x = condition,
      dir = "two.sided")
```

Overall
```{r}
## Overall
df2 %>%
  as.data.frame() %$%
  ttestBF(cond_dp,
          mu = 0,
          nullInterval = c(0, Inf)) %>%
  printBFt()
ttest(data = df2,
      y = cond_dp,
      x = condition,
      mu = 0,
      dir = "greater")
```




## Confidence

*How confident (in %) are you that you can make a reasonable estimate?*

Left : 0 |----------| 100  
Right: 0 |----------| 100  

```{r}
# Graph
df2 %>%
  ggplot(aes(x = condition,
             y = conf_dp,
             fill = condition)) +
  geom_violin() + 
  stat_summary(fun.data = "mean_sdl", geom = "crossbar", width = 0.2, fun.args = list(mult = 1)) +
  geom_jitter(size = 0.5, width = 0.2) +
  geom_hline(yintercept = 0, linetype = 2) +
  scale_fill_manual(values = pal) +
  theme_apa() +
  labs(x = "Condition",
       y = "Confidence estimates") +
  theme(legend.position = "none")
```

```{r}
### Descriptives
df2 %>%
  group_by(condition) %>%
  summarize(M = printnum(mean(conf_dp)),
            SD = printnum(sd(conf_dp))) %>%
  knitr::kable(caption = "Confidence estimates", digits = 2) %>%
  kable_styling(bootstrap_options = "hover", full_width = F, position = "center")
```

```{r}
### Test
df2 %>%
  as.data.frame() %>%
  ttestBF(formula = conf_dp ~ condition,
          nullInterval = c(-Inf, Inf),
          data = .) %>%
  printBFt()
ttest(data = df2,
      y = conf_dp,
      x = condition,
      dir = "two.sided")
```


## Demographic data

Our participants:
```{r}
# Summary of most relevant demographic data
df2 %>%
  summarise(N = n(),
            female = length(which(gender == "female")),
            age_mean = mean(age, na.rm = TRUE),
            age_sd = sd(age, na.rm = TRUE),
            Psychstudents_percent = length(which(psych == "Yes")) / n() * 100) %>%
  knitr::kable(caption = "Demographic data", digits = 2) %>%
  kable_styling(bootstrap_options = "hover", full_width = F, position = "center")
```

And their level of education:
```{r}
# Level of education
df2 %>%
  group_by(edu) %>%
  summarise(count = length(edu)) %>%
  knitr::kable(caption = "Level of education", digits = 2) %>%
  kable_styling(bootstrap_options = "hover", full_width = F, position = "center")
```

## Counterbalancing check

This tab is mainly for me to make sure I got the recoding of all the counterbalancing right.

Regression of recoded factors on raw scores:  

Preference
```{r}
# Preference
summary(lm(pref_raw ~ condition * primacy, data = df2))
```

Impression
```{r}
# Impression
summary(lm((impr_l_raw - impr_r_raw) ~ condition * primacy, data = df2))
```

Conditionals
```{r}
# Conditionals
summary(lm((cond_l_raw - cond_r_raw) ~ condition * primacy, data = df2))
```

